SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-13 paper/pm-1-matrix.tex
new figure

\end{tikzpicture}  
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \tikzset{
    ln/.style  = { draw, thick, fill=black, circle, inner sep=0.3mm},
    sqloc/.style  = { draw, thick, inner sep=1.0mm },
    loc/.style    = { draw, circle, thick, inner sep=1.0mm },
  }
\begin{tikzpicture}
  \node[draw] (n0) {$n_1:\{0,1,2,3,4\}$};
  \node[draw,below left of=n0] (n1) {$n_1:\{0,1,2,3,4\}$};
  \node[draw] (n2) {$n_1:\{0,1,2,3,4\}$};

    \entity[yshift=-20mm] (E) {$n_1$ $[m_0 m_1 m_2 m_3 m_4]$};
    % \entity (E) {Node1\\[]};
    \binary[left=of E.north west, unique=2] (h) {};

       % \binary[left=of E.north west, unique=1-2] (w) {};

    \binary[left=of E.south west, unique=1-2](i) [below=6mm of h]{};
    \node[role name, at=(i.north),anchor=south] {[$m_{0} m_{1} m_{3}$]};
    \plays[] (E) to (i.east);
   % \plays(h) to (i);
%         label=below:\ormleft{uses] (u) {};
\node[role name,
at=(h.north),anchor=south] {[$m_{0} m_{1}$]};

    \entity[left=of h] (Rank) {$n_0:m_0 m_1 m_2 m_3 m_6$};

    \plays[mandatory] (E) to (h.east);
    \plays (h) to (Rank) (E);
    \plays[mandatory] (Rank) to (i.west);
    %to (u.east) (u) to (Car);

    \binary[right=of E.north east] (b) {};
    \node[role name,
at=(b.north),anchor=south] {[$m_{0} m_{1}$]};
       % \binary[right=of E.north east] (dd) {};

    \binary[right=of E.south east, unique,] (i) {};
    \node[role name,
at=(i.north),anchor=south] {[$m_{1} m_{2} m_{3}$]};
\binary[unique=1-2,skip unique=1-2] (xyz) [above=6mm of h] {};
% describes blue label above h Left uppermost
\node[role name,
at=(xyz.north),anchor=south] {[$m_{0} m_{1} m_{3}$]};

      \plays (Rank) to (xyz.west); 
    \plays[mandatory] (E) to (xyz.east);

    \entity[right=1.8 of E] (Date) {$n_2: m_1 m_2 m_3 m_6 m_8$};

    \plays[mandatory] (E) to (b.west); 
    \plays (E) to (i.west);
    \plays (b.east) to (Date);
    \plays[mandatory] (Date) to (i.east);

%    \entity[label={[constraint]\#=$n$}] {E};
%\draw (Rank) to node[vroles,label=has,label=below:\ormup{of}]{} (E);
%\node[constraint,anchor=north west,inner ysep=0]
%at (h.) {\ormbraces{a, b, c}};
%\draw (E) to node[roles,
%label=below:drives]{} (Rank);

\node[roles=2][,unique=1-2,skip unique=2] (abc) [below=11mm of E] {};
\node[role name,
at=(abc.north),anchor=south] {[$m_{2} m_{3}$]};
\plays[mandatory] (Rank.south) -- (abc.west);  
\plays (abc.east) -- (Date.south);

  %  \node[role name, anchor=south west] at (b.east) {[birthdate]};
  %  \node[role name, anchor=north west] at (i.east) {[hiredate]};

%     \rules at (-.4, -2) {
%          \node[rule=1] {{$m_{2}$} $m_{3}$};\\
%      };
\end{tikzpicture}
\end{minipage}

>>>>

\end{tikzpicture}  
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \tikzset{
    ln/.style  = { draw, thick, fill=black, circle, inner sep=0.3mm},
    sqloc/.style  = { draw, thick, inner sep=1.0mm },
    loc/.style    = { draw, circle, thick, inner sep=1.0mm },
  }
\begin{tikzpicture}[node distance = 30mm]
  \node[draw] (n0) {$n_1:\{01234\}$};
  \node[draw,below left of=n0] (n1) {$n_0:\{01236\}$};
  \node[draw,below right of=n0] (n2) {$n_2:\{012368\}$};

  \draw[->,thick] (n1) -- node[left=1mm]  {$01$} (n0);
  \draw [->,thick] (n1) to [bend right=-30] node[left=1mm]  {$013$} (n0);
  \draw [->,thick] (n0) to [bend right=-30] node[below=2pt,xshift=3pt]  {$013$} (n1);

  \draw [->,thick] (n1) -- node[below=1mm]  {$123$} (n2);
  \draw [->,thick] (n2) to [bend right=-45] node[below=2pt]  {$01$} (n1);

  \draw [->,thick] (n2) -- node[left=2pt]  {$23$} (n0);

\end{tikzpicture}
\end{minipage}
